---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# mbc

The goal of mbc is to make comparisons between different code expressions.
It builds on the R package microbenchmark, adding a comparison of
the output provided by each expression in addition to the comparison
of run time as given by microbenchmark.

## Installation

You can install mbc from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CollinErickson/mbc")
```

## Example

This is a basic example which shows you how to solve a common problem.
It creates random samples of 100 exponential data points and finds the
mean or median. The results show that the mean is 4 times faster
(since it doesn't have to sort the values) and that the mean
is around 1 while the median is around 0.71.

```{r example}
## basic example code
mbc::mbc(mean(rexp(100)), median(rexp(100)))
```
